Ellipsoids (v1.0): 3D Magnetic modelling of ellipsoidal bodies

### 2017-06-05 manuscript/manuscript.tex
Correcao ortografica - a free... Exclusao de -there are some commercial... na introducao. Notebook para verificar o ponto 3 do comentario da revisao.

A vast literature about the magnetic
modelling of ellipsoidal bodies was developed in which
are to be found the names of many researchers.
Nevertheless, interest in this subject has not yet died
out, as is evidenced by a list of modern papers in this
field.
Besides, the geoscientific community lacks an free easy-to-use
tool to simulate the magnetic field produced by uniformly
magnetized ellipsoids. There are some commercial software
packages that includes the ellipsoid model, but all very
expensive.
Such a tool could prove to be useful either for teaching
and researching geophysics.

>>>>

A vast literature about the magnetic
modelling of ellipsoidal bodies was developed in which
are to be found the names of many researchers.
Nevertheless, interest in this subject has not yet died
out, as is evidenced by a list of modern papers in this
field.
Besides, the geoscientific community lacks a free easy-to-use
tool to simulate the magnetic field produced by uniformly
magnetized ellipsoids. Software packages that includes the 
ellipsoid model exist, but all very expensive.
Such a tool could prove to be useful either for teaching
and researching geophysics.
